\documentclass{article}
\usepackage{listings}
\usepackage{titling}

\setlength{\droptitle}{-10em}   % This is your set screw

\begin{document}

\title{Project Proposal}
\author{David Kohlbrenner, Benjamin Braun}
\maketitle


\section{Outline}
We will be building a virtual machine for the purpose of providing a
platform to teach practical cryptographic attacks. The VM will contain
a webpage listing available problems, descriptions, and
hints. Problems will be (mostly) drawn from the competitive hacking
community (CTF), which writes many problems of this style every year.

Problems will be pulled in, cleaned up, modified for our VM, given
detailed descriptions, and properly attibuted.

Each problem will consist of either text (usually ciphertexts,
signatures, etc) or a service running on a socket. To solve a problem,
each problem contains a ``flag'' (either a plaintext, or a recovered
secret key, etc).

Problems will require users to implement various cryptographic
attacks, ranging from factoring small primes, known RSA attacks, hash
extension, padding oracle attacks, to known broken cryptosystems.

\section{Deliverables}
A github repo and vagrant script for generating the virtual machine.

The VM will have a webserver serving a welcome and overview page, a
suggested tools page, and the problems and categories.

The VM will contain several categories of problems, including (but not limited to):
\begin{itemize}
\item ``Bad'' RSA implementations
\item Modular arthimatic (not directly RSA)
\item Other (obscure) Public Key Systems
\item Hashing attacks
\end{itemize}

Each problem will have
\begin{itemize}
\item A description (possibly with flavor)
\item A list of relevant topics or skills
\item A way to check if your solution is correct (a ``flag'')
\item Possibly a full solution, or link to solution as available elsewhere
\end{itemize}

\end{document}
